---
title: "Untitled"
author: "Amal Kallendherry"
date: "2023-03-20"
output: pdf_document
---
## Put comments here that give an overall description of what your
## functions do. 

## Write a short comment describing this function
##The first function, makeCacheMatrix creates a special “matrix”, which is really a list containing a function to:
###set the elements of the matrix
###get the elements of the matrix
###set the elements of the matrix inverse
###get the elements of the matrix inverse

```{r}
makeCacheMatrix <- function(x = matrix()) {
  invs <- NULL
  set <- function(y) {
    x <<- y
    invs <<- NULL
  }
  get <- function() x
  setinverse <- function(inverse) invs <<- inverse
  getinverse <- function() invs
  list(set = set, get = get,
       setinverse = setinverse,
       getinverse = getinverse)
}
```


## Write a short comment describing this function
###The following function calculates the inverse of the special “matrix” created with the above function. However, it first checks to see if the inverse has already been calculated. If so, it gets the inverse from the cache and skips the computation. Otherwise, it calculates the inverse of the matrix and sets it in the cache via the setinverse function.

```{r}
cacheSolve <- function(x, ...) {
  invs <- x$getinverse()
  if(!is.null(invs)) {
    message("getting cached data")
    return(invss)
  }
  matrix_to_invert <- x$get()
  invs <- solve(matrix_to_invert, ...)
  x$setinverse(invs)
  invs
}
```

